Make any stupid plot you want

### 2020-12-24 draft/sections/math.tex
forget new packages + formatting

\subsubsection {Example: Matplotlib Visual Fiber}
For example, for Matplotlib \cite{hunterMatplotlib2DGraphics2007}, some of the possible types in $P$ are:
\begin{table}[ht]
    \renewcommand{\arraystretch}{2}
    \begin{tabulary}{\textwidth}{|l|C|L|}\hline
     $\nu_{i}$                      & $\mu_{i}$                                                            & $dom(\nu_{i})$  \\ \hline                                              
    position                    & x, y, z                                                          & $\mathbb{R}$   \\ \hline
    size                        & linewidth, markersize                                            & $\mathbb{R}$   \\ \hline
    shape                       & markerstyle                                                      & $((\mathbb{R}, \mathbb{R}), x \in \{0,1,2,3,4,79\})^{n}^{\dag}$ \\ \hline
    color                       & color, colors, linecolor, facecolor, markerfacecolor, edgecolor  & $\mathbb{R}^4$ \\ \hline
    \multirow{2}{*}{texture}    & hatch                                                            & $/^*\backslash^*-^*+^*x^*o^*O^*.^**^* \in \Sigma^{+}$ \newline $\Sigma=\{/, \backslash, |, -, +, x, o, O, ., *\}^{\ddag}$\\\cline{2-3}
                                & linestyle                                                        & $(\mathbb{Z}, (\mathbb{Z}^n))^{\dag}$ \\ \hline              
    \end{tabulary}
    \caption{\\
        \footnotesize{\dag $n>0$}\\
        \footnotesize{\ddag$\Sigma^+=\cup_{n\in\mathbb{Z}^+}\Sigma^n$}

    }
\end{table}

>>>>

\subsubsection {Example: Matplotlib Visual Fiber}
For example, for Matplotlib \cite{hunterMatplotlib2DGraphics2007}, some of the possible types in $P$ are:
\begin{table}[ht]
    \label{tab:mpl_visual_variable_fiber}
\begin{threeparttable}
    \renewcommand{\arraystretch}{2}
    \begin{tabulary}{\textwidth}{|l|L|L|}\hline
     $\bm{\nu_{i}}$                      & $\bm{\mu_{i}}$                                                            & $\bm{dom(\nu_{i})}$  \\ \hline                                              
    position                    & x, y, z                                                          & $\mathbb{R}$   \\ \hline
    size                        & linewidth, markersize                                            & $\mathbb{R}$   \\ \hline
    shape                       & markerstyle                                                      & $((\mathbb{R}, \mathbb{R}), x \in \{0,1,2,3,4,79\})^{n}$\tnote{\dag} \\ \hline
    color                       & color, colors, linecolor, facecolor, markerfacecolor, edgecolor  & $\mathbb{R}^4$ \\ \hline
    \multirow{2}{*}{texture}    & hatch                                                            & $/^*\backslash^*-^*+^*x^*o^*O^*.^**^* \in \Sigma^{+}$ \newline $\Sigma=\{/, \backslash, |, -, +, x, o, O, ., *\}$ \tnote{\ddag}\\\cline{2-3}
                                & linestyle                                                        & $(\mathbb{Z}, (\mathbb{Z}^n))$\tnote{\dag} \\ \hline              
    \end{tabulary}
    \begin{tablenotes}\footnotesize
        \item[\dag] $n>0$
        \item[\ddag]$\Sigma^+=\cup_{n\in\mathbb{Z}^+}\Sigma^n$
    \end{tablenotes}

\end{threeparttable}
\end{table}
